Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 implementation.tex
fixed acronym spacing
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1065 ccdd05d5-56c1-461a-bf98-85f6876523b4
Moved sentence from decimation section to basis filters section
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1099 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added 'queues'
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1100 ccdd05d5-56c1-461a-bf98-85f6876523b4

The whitened detector data is reduced to successively
lower sample rates by decimation. Decimation involves applying an anti-aliasing
filter to the data, and then down-sampling by deleting samples.  We use a
192-tap \fir\ decimator provided by \gstreamer{}'s {\tt audioresample}
element.  The detector data is provided at every power-of-two sample rate
required by the time slices described in \eqref{eq:time-slices}.  At this point,
the \gstreamer\ pipeline splits into several parallel branches to handle each
time slice.  Next, these decimated data streams are fed into parallel \fir\ filter banks.

@@

The basis filters are implemented using a \gstlal\ element called {\tt
lal\_firbank}, which provides a single input, multiple output bank of \fir\ filters
from a matrix of filter coefficients.  Several instances of {\tt lal\_firbank}
execute in parallel to handle each of the time slices.  Filter coefficients are taken
from the nonzero samples of the time slices in equation~\eqref{eq:time-sliced-templates},
with the zero-padding effectively accomplished by appropriate delays.

@@

From the outputs of the \SVD\ basis filters, we form the partial \SNR streams for
each time  slice by multiplying by the reconstruction matrices.  This is accomplished
with the \texttt{gstlal} element \texttt{lal\_matrixmixer}.

>>>>

The whitened detector data is reduced to successively
lower sample rates by decimation. Decimation involves applying an anti-aliasing
filter to the data, and then down-sampling by deleting samples.  We use a
192-tap \fir\ decimator provided by \gstreamer{}'s {\tt audioresample}
element.  The detector data is provided at every power-of-two sample rate
required by the time slices described in \eqref{eq:time-slices}.  At this point,
the \gstreamer\ pipeline splits into several parallel branches to handle each
time slice.

@@

Next, these decimated data streams are fed into parallel \fir\ filter banks.
The basis filters are implemented using a \gstlal\ element called {\tt
lal\_firbank}, which provides a single input, multiple output bank of \fir\ filters
from a matrix of filter coefficients.  Several instances of {\tt lal\_firbank}
execute in parallel to handle each of the time slices.  Filter coefficients are taken
from the nonzero samples of the time slices in equation~\eqref{eq:time-sliced-templates},
with the zero-padding effectively accomplished by appropriate queues, or delay lines.

@@

From the outputs of the \SVD\ basis filters, we form the partial \SNR\ streams
for each time  slice by multiplying by the reconstruction matrices.  This is
accomplished with the \texttt{gstlal} element \texttt{lal\_matrixmixer}.
